Paper 1: Instrument development

### 2024-09-02 Rmd/Paper1.Rmd
Final version for the day?

---
title: "Paper 1: Instrument development"
author: "Niklas Karlsen, OsloMet, Norway, e-mail: niklaska@oslomet.no"
date: "2024-05-28"
bibliography: "../data/meta_data/references.bib"
csl: "../scripts/university-of-gothenburg-apa-7th-edition-swedish-legislations.csl" # (source: https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html)
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true

@@

@@

@@

>>>>

---
title: "Paper 1: Instrument development"
author: "Niklas Karlsen, OsloMet, Norway, e-mail: niklaska@oslomet.no"
date: "2024-09-02"
bibliography: "../data/meta_data/references.bib"
csl: "../scripts/university-of-gothenburg-apa-7th-edition-swedish-legislations.csl" # (source: https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html)
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true

@@

These are the libraries we use for special functions.

@@

Clean the data in the different datasets, so they can be more easily compared. Differences in question formulations between datasets are adjusted so they are the same. Missing information (covariates) is added when it is known.

@@

Item labels are given based on the intended TPACK-structure when the items were created.
